---
title: "Reproducibility Workshop"
subtitle: ""
author: "[Dani Cosme](https://dcosme.github.io/)"
output:
  xaringan::moon_reader:
    css: ["default", "css/dcos.css", "css/dcos-fonts.css"]
    lib_dir: libs
    nature:
      highlightStyle: atelier-lakeside-light
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE, 
  comment = NA, dpi = 300,
  fig.align = "center", out.width = "80%", cache = FALSE)

if(!require('tidyverse')) {
	install.packages('tidyverse')
}
if(!require('devtools')) {
	install.packages('devtools') 
}
if(!require('emo')) {
	devtools::install_github("hadley/emo")
}
if(!require('xaringanExtra')) {
	devtools::install_github("gadenbuie/xaringanExtra")
}
if(!require('countdown')) {
	devtools::install_github("gadenbuie/countdown")
}
```

## The reproducibility crisis

--

Text

* 

---

## Reproducibility versus replicability

--

Text

* 

---

## Reproducible workflows

--

* Whole project, start to finish

--

* 

---

## Reproducible workflows

```{r errors, echo=FALSE}
xaringanExtra::use_editable(expires = 1)
```

### What parts of your current workflow are prone to human error?

.pull-left[
  .can-edit.key-likes[
  - 
  ]
]

.pull-right[
  .can-edit.key-likes[
  - 
  ]
]

---

## Reproducible workflows
```{r workflows, echo=FALSE}
xaringanExtra::use_editable(expires = 1)
```

### What makes a workflow reproducible?

.pull-left[
  .can-edit.key-likes[
  - 
  ]
]

.pull-right[
  .can-edit.key-likes[
  - 
  ]
]


---

## Reproducible reporting with Rmarkdown

--

Text

* 

---

## Project example

```{r echo=FALSE, out.width=750}
knitr::include_url("https://cnlab.github.io/self-social-sharing/")
```

`r emo::ji("link")` Click [here](https://github.com/cnlab/self-social-sharing) to access the project 


---

## Reproducible report walk-through

--

Text

* 

---

## Extensions

--

* Version control using [`git`]() and [`github`]()

--

* Static website hosting with [`github`]()

--

* Interactive data visualization and communication using [`{shiny}`

---
