---
title: "Reproducible report template"
author: "Dani cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
# set chunk options for the document
# include=FALSE means that this chunk will not show up in the report

knitr::opts_chunk$set(echo = TRUE, dpi = 150, fig.path = "figs/") 
# echo = TRUE means that the source code will be displayed
# dpi = 150 sets the figure resolution
# fig.path specifies a directory where figures will be output

options(scipen = 999) #turn off scientific notation
set.seed(65) #set seed for random number generation
```

Text describing the project


# Prep {.tabset}
## Load packages
```{r, message=FALSE}
if (!require(pacman)) {
  install.packages('pacman')
}
pacman::p_load(devtools, report, install = TRUE)
devtools::install_github("hadley/emo")
```

## Define aesthetics
```{r}

```

## Define functions
```{r}

```

## Load data
```{r}

```

## Tidy data
* Describe transformations made to the data
* Describe participant and datapoint exclusions

```{r}

```

# Sample demographics {.tabset}
For this tutorial, these are made up demographics to illustrate how to summarize and present different characteristics

## Sample size

```{r}

```

## Geographic distribution
```{r}

```

## Age
```{r}

```

## Gender
```{r}

```

## Race and ethnicity
```{r}

```

# Data quality checks {.tabset}
## Missing data
```{r}

```

## Outliers
```{r}

```


# Descriptive statistics {.tabset}
Describe the items and scales used

## Ns, means, and standard deviations
```{r}

```

## Correlations among variables
```{r}

```

# Visualize raw data {.tabset}
## Distributions
```{r}

```

# Preregistered or confirmatory analyses {.tabset}
## Hypothesis 1 {.tabset}
> Hypothesis text

**Results**

`r emo::ji("check")` 

```{r}

```

### plot
```{r}

```

### model table
```{r}

```

### summary
```{r}

```

### check model
Check model assumptions using the [`{performance}` package](https://easystats.github.io/performance/)
```{r}

```

## Hypothesis 2 {.tabset}
> Hypothesis text

**Results**

`r emo::ji("check")` 

```{r}

```

### plot
```{r}

```

### model table
```{r}

```

### summary
```{r}

```

### check model
Check model assumptions using the [`{performance}` package](https://easystats.github.io/performance/)
```{r}

```

# Post-hoc or exploratory analyses {.tabset}
## Research question 1 {.tabset}
> Research question text

**Results**

`r emo::ji("check")` 

```{r}

```

### plot
```{r}

```

### model table
```{r}

```

### summary
```{r}

```

### check model
Check model assumptions using the [`{performance}` package](https://easystats.github.io/performance/)
```{r}

```

# Package citations
```{r}
report::cite_packages()
```

# Resources
## Reproducible reports in R
* [Improve your workflow for reproducible science - Mine Çetinkaya-Rundel](https://mine-cr.com/talk/2021-improve-workflow-repro-science-oss/)
* [R Markdown for writing reproducible scientific papers - Mike Frank & Chris Hartgerink](https://libscie.github.io/rmarkdown-workshop/handout.html)
* [R Markdown for scientists - Nicholas Tierney](https://rmd4sci.njtierney.com/)
* [Reproducible Analysis with R](https://nceas.github.io/sasap-training/materials/reproducible_research_in_r_fairbanks/)
* [Reproducible science curriculum](https://github.com/Reproducible-Science-Curriculum)

## R Markdown
* [R Markdown](https://rmarkdown.rstudio.com/lesson-1.html)
* [R Markdown reference guide](https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf?_ga=2.245086913.571798724.1647284447-1046469491.1644870105)

## Themes
* [R Markdown theme gallery](https://www.datadreaming.org/post/r-markdown-theme-gallery/)
* [{rmdformats} theme package](https://juba.github.io/rmdformats/)

